---
title: "Comparison: Das Gupta & Horiuchi"
format: html
editor_options: 
  chunk_output_type: console
execute:
  warning: false
  message: false
---

```{r}
#| include: false
file.copy("dgh_res1.rdata","docs/dgh_res1.rdata")
file.copy("dgh_res2.rdata","docs/dgh_res2.rdata")
file.copy("dgh_res3.rdata","docs/dgh_res3.rdata")
file.copy("dgh_res4.rdata","docs/dgh_res4.rdata")
```


This documents provides some comparisons of the Horiuchi and Das Gupta methods of decomposition, as implemented in **{{DemoDecomp}}** and **{{DasGuptR}}** respectively. 

First, it shows for a simple decomposition of a rate as the product of four factors, that the two approaches converge as the number of integration steps for the Horiuchi method increases. 
It then demonstrates that the number of factors and the numbers of subgroups create little divergence between the two methods, nor does the size of the crude rate difference being decomposed. 

Finally, it provides a discussion of subgroup specific contributions as calculated via the two methods.  

# 1. Setup and functions

```{r}
#| code-fold: true
library(tidyverse)
library(DemoDecomp)
library(DasGuptR)


## Data sim --- 
# Two populations, nK factors, nI subgroups,
# difference in crude rates should be ~0.05
simdata <- function(nK = 3, nI = 5, crude_delta = 0.05) {
  # subgroup size:
  wA = rgamma(nI, shape = 2, scale = 1000)
  # subgroup prop:
  pA = wA / sum(wA)
  
  # have f1 be a baseline rate: 
  fA1 = rbeta(nI, shape1 = 3, shape2 = 50) 
  # make f2..k multipliers of relative risk, ~1
  if(nK > 1) {
    fA2k = rlnorm(nI * (nK - 1), meanlog = 0, sdlog = 0.25)
    fA = c(fA1, fA2k)
  } else {
    fA = fA1
  }
  
  
  # pop B is initially pop A:
  pB = pA
  fB = fA
  
  # add some shift:
  pB = pA + rnorm(nI, mean = 0, sd = 0.02)
  # needs to be bounded
  pB = pmax(pB, 0.001) / sum(pmax(pB, 0.001))
  # F1 will increase by crude_delta on avg. 
  # F2..k are es
  fB[1:nI] <- 
    pmax(
      fB[1:nI] + crude_delta + rnorm(nI, mean = 0, sd = crude_delta*.1), 
      .0001
      )
  if (nK > 1) {
    fB[(nI+1):length(fB)] <- fB[(nI+1):length(fB)] * 
      rlnorm(nI * (nK - 1), meanlog = 0, sdlog = 0.05)
  }
  
  return(list(
    popA = c(pA, fA),
    popB = c(pB, fB),
    nK = nK,
    nI = nI
  ))
}



## Das Gupta decomposition --- 
getDG <- function(sdata){
  require(DasGuptR)
  # dgnpop needs a data frame,
  # and population indicator etc. 
  dfdg <- cbind(
    pop = rep(letters[1:2],e=sdata[[4]]),
    sgroup = rep(1:sdata[[4]],2),
    rbind(
      as.data.frame(matrix(sdata[[1]],ncol=sdata[[3]]+1)),
      as.data.frame(matrix(sdata[[2]],ncol=sdata[[3]]+1))
    )
  )

  ## decomp:
  if(sdata[[4]]==1){
    # subgroup size not included if only 1 subgroup
    flist = names(dfdg)[-c(1:3)] 
  } else{
    flist = names(dfdg)[-c(1:2)] 
  }
  
  dg_res = 
    dg_table(dgnpop(dfdg,
         pop = "pop", 
         factors = flist,
         id_vars = "sgroup",
         quietly = FALSE,
         ratefunction = 
           paste0("sum(",paste0(flist,collapse="*"),")")
  ))$diff
  
  return(
    # remove the crude diffs:
    dg_res[-length(dg_res)]
  )
}

## Horiuchi decomposition --- 
getH <- function(sdata, nstep=100){
  require(DemoDecomp)
  # horiuchi just wants vectors
  pop1 = sdata[[1]]
  pop2 = sdata[[2]]
  
  # rate function
  if(sdata[[4]]==1){
    
    aggrfunc = function(x){
      x <- matrix(x, ncol = sdata[[3]])
      sum(matrixStats::rowProds(x))
    }
    # decomposition:
    hres <- horiuchi(func = aggrfunc,
                   pars1 = pop1[-1],
                   pars2 = pop2[-1],
                   N = nstep)
    hres <- matrix(hres, ncol = sdata[[3]])
    
  } else {
    
    aggrfunc = function(x){
      x <- matrix(x, ncol = sdata[[3]]+1)
      sum(matrixStats::rowProds(x))
    }
    # decomposition:
    hres <- horiuchi(func = aggrfunc,
                   pars1 = pop1,
                   pars2 = pop2,
                   N = nstep)
    hres <- matrix(hres, ncol = sdata[[3]]+1)
    
  }

  return(
    colSums(hres)
  )
}
```


## 2. Number of integration steps

For this example, we set the number of factors = 4, and the number of subgroups = 1. 
The rate is a simple product of the 4 factors, where the crude rate difference is set to approximately .05 (rates are expressed as proportions).  
We vary the number of integration steps in Horiuchi (the `N` argument to `horiuchi()` function), from 1 to 100. 
For each number of integration steps, we sim 50 datasets and perform decomposition using both `DasGuptR::dgnpop()` and `DemoDecomp::horiuchi()`.  


```{r}
#| eval: false
#| code-fold: true
# set up conditions and n sims
res1 <- 
  expand_grid(
    nsteps = c(1:25,seq(30,100,5)),
    sims = 1:50
  )

# for each sim, get decomposition effects from 
# both DG and H methods
res1$data <- res1$DG <- res1$H <- NA
for(i in 1:nrow(res1)){
  res1$data[i] <- list(simdata(nK=4,nI=1))
  res1$DG[i] <- list(getDG(res1$data[[i]]))
  res1$H[i] <- list(getH(res1$data[[i]], res1$nsteps[[i]]))
}

res1 <- res1 |> unnest(c(DG,H))

save(res1, file = "dgh_res1.rdata")
```


```{r}
#| code-fold: true
load(url("https://dasguptr.github.io/dgh_res1.rdata"))

cbind(
  nsteps = c(1:25,seq(30,100,5)),
  rmse = tapply((res1$H - res1$DG)^2, 
                res1$nsteps, 
                \(x) sqrt(mean(x))
                )
  ) |> 
  ggplot(aes(x=nsteps, y=rmse)) +
  geom_point()+geom_line()+
  labs(y = "root mean squared diff\nHoriuchi - Das Gupta")
```

## 3. Number of factors

For Das Gupta's approach, increasing the number of factors involves increased computation time, as it means evaluating the rate at many more combinations of factors.  

Below, we vary the number of factors from 1 to 10, again with just a single subgroup, and a crude rate difference of ~.05.  
In each case, the rate is calculated as a simple product of all factors, and we use 100 integration steps for Horiuchi.  
For each number of factors, we simulate 50 datasets.  
```{r}
#| eval: false
#| code-fold: true
# set up conditions and n sims
res2 <- 
  expand_grid(
    nf = c(2:10),
    sims = 1:50
  )

# for each sim, get decomposition effects from 
# both DG and H methods
res2$data <- res2$DG <- res2$H <- NA
for(i in 1:nrow(res2)){
  res2$data[i] <- list(simdata(nK=res2$nf[i], nI=1))
  res2$DG[i] <- list(getDG(res2$data[[i]]))
  res2$H[i] <- list(getH(res2$data[[i]], nstep = 100))
}

res2 <- res2 |> unnest(c(DG,H))
save(res2, file = "dgh_res2.rdata")
```


```{r}
#| code-fold: true
load(url("https://dasguptr.github.io/dgh_res2.rdata"))

cbind(
  nf = c(2:10),
  rmse = tapply((res2$H - res2$DG)^2, 
                res2$nf, 
                \(x) sqrt(mean(x))
                )
  ) |> 
  ggplot(aes(x=nf, y=rmse)) +
  geom_point()+geom_line()+
  labs(y = "root mean squared diff\nHoriuchi - Das Gupta",
       x = "number of factors")
```


## 4. Number of subgroups: 

Finally, we vary the number of subgroups from 2 to 50. 
In each case, the rate is calculated as the product of 2 factors (subgroups relative sizes, and a subgroup specific value such as a subgroup specific rate), and we use 100 integration steps for Horiuchi.  
For each number of subgroups, we simulate 50 datasets.  

Here we are only comparing the divergence in the marginal effects of each factor (i.e., the sum of the subgroup specific contributions).  

```{r}
#| eval: false
#| code-fold: true
res3 <- 
  expand_grid(
    nsubgroup = c(2:50),
    sims = 1:50
  )

res3$data <- res3$DG <- res3$H <- NA
for(i in 1:nrow(res3)){
  res3$data[i] <- list(simdata(nK=1,nI=res3$nsubgroup[i]))
  res3$DG[i] <- list(getDG(res3$data[[i]]))
  res3$H[i] <- list(getH(res3$data[[i]], nstep = 100))
}

res3 <- res3 |> unnest(c(DG,H))
save(res3, file="dgh_res3.rdata")
```

```{r}
#| code-fold: true
load(url("https://dasguptr.github.io/dgh_res3.rdata"))

cbind(
  nsubgroup = c(2:50),
  rmse = tapply((res3$H - res3$DG)^2, 
                res3$nsubgroup, 
                \(x) sqrt(mean(x))
                )
  ) |> 
  ggplot(aes(x=nsubgroup, y=rmse)) +
  geom_point()+geom_line()+
  labs(y = "root mean squared diff\nHoriuchi - Das Gupta")
```


## 5. Crude rate difference 

Note that these differences will grow ever so slightly the bigger the crude-rate differences are, but these are always minimal (<1e-6)

```{r}
#| eval: false
#| code-fold: true
# set up conditions and n sims
res4 <- 
  expand_grid(
    cdiff = seq(0,1,length.out=20),
    sims = 1:50
  )

# for each sim, get decomposition effects from 
# both DG and H methods
res4$data <- res4$DG <- res4$H <- NA
for(i in 1:nrow(res4)){
  res4$data[i] <- list(simdata(nK=4,nI=1,crude_delta=res4$cdiff[i]))
  res4$DG[i] <- list(getDG(res4$data[[i]]))
  res4$H[i] <- list(getH(res4$data[[i]], 100))
}

res4 <- res4 |> unnest(c(DG,H))
save(res4, file="dgh_res4.rdata")
```

```{r}
#| code-fold: true
load(url("https://dasguptr.github.io/dgh_res4.rdata"))

cbind(
  cdiff = seq(0,1,length.out=20),
  rmse = tapply((res4$H - res4$DG)^2, 
                res4$cdiff, 
                \(x) sqrt(mean(x))
                )
  ) |> 
  ggplot(aes(x=cdiff, y=rmse)) +
  geom_point()+geom_line()+
  labs(y = "root mean squared diff\nHoriuchi - Das Gupta",
       x = "crude rate difference")
```


## 6. subgroup specific effects and sum-to-1 constraints

Here we demonstrate how it is possible to reparameterize Horiuchi by dropping any given subgroup proportion to obtain different subgroup specific contributions (all relative to the omitted group), but preserve the overall marginal totals. 
We also show that this is not possible in Das Gupta's method - it is possible to omit a subgroup proportion but this makes no change to the decomposition process.  
For this demonstration, we will use Das Gupta's Example 5.1, which contains, for 2 populations, a set of 13 age groups, the age-specific rates, and their relative size as a percentage.  
A quick plot of the age group sizes shows that, e.g.: the 15-19 group makes up a bigger proportion of the 1st population than the 2nd; this is reversed in the 25-29 group; and the 60-64 group makes up a similar proportion in both populations:  

```{r}
# express subgroup size as proportions (currently %)
df <- dgeg5_1 |> mutate(size=size/100)

ggplot(df,aes(x=pop,y=size))+
  geom_point()+geom_line(group=1)+
  facet_wrap(~age_group)
```

Performing decomposition with `DemoDecomp::horiuchi()` requires providing the values as vectors of length K*I (where K is number of factors, I is number of subgroups): 

```{r}
# population weights and rates as vectors for horiuchi()
pop1 = c(df$size[df$pop==1970],df$rate[df$pop==1970])
pop2 = c(df$size[df$pop==1985],df$rate[df$pop==1985])

# this is the rate function for decomposition using full vector: 
aggrfunc_full <- function(x){
  ws = x[1:13]
  rs = x[14:26]
  sum(ws*rs)
}

hres0 <- horiuchi(func = aggrfunc_full,
                  pars1 = pop1,
                  pars2 = pop2,
                  N = 100)
```

The overall factor contributions (age-proportions and age-specific rates) are obtained by summing over the subgroups:  
```{r}
sum(hres0[1:13]);sum(hres0[14:26])
```

We can see that these are equivalent to what we get out of `DasGuptR::dgnpop()` (the `diff` column of the table below): 
```{r}
dgnpop(df, pop="pop", 
       factors=c("size","rate"),
       ratefunction = "sum(size*rate)") |>
  dg_table()
```

To get subgroup specific effects from `dgnpop()`, we need to set `agg = FALSE` as well as removing the aggregating `sum()` from the rate function.  
```{r}
dgres0 <- 
  dgnpop(df, pop="pop", 
         factors=c("size","rate"),
         id_vars = "age_group",
         ratefunction = "size*rate", 
         agg=FALSE) 

# to get these into the same format as horiuchi: 
dgres0 <- 
  dgres0[,-3] |>
  pivot_wider(names_from=factor,values_from=rate) |>
  pivot_wider(names_from=pop,values_from=c(size,rate)) |>
  transmute(
    size = size_1985-size_1970,
    rate = rate_1985-rate_1970
  )
```

Just as with Horiuchi, the overall factor contributions can be retrieved by summing over the subgroups: 
```{r}
colSums(dgres0)
```

And the subgroup specific values are the same for the two methods:
```{r}
cbind(
  dgres0,
  hres0[1:13],
  hres0[14:26]
) |> plot()
```

Because subgroup proportions must sum to 1, we can omit a group from the vector, and provide this as part of the function.  

For `horiuchi()`, we need to adjust the function to insert the missing value in the appropriate place in the vector:  
```{r}
aggrfunc_sub <- function(x, idx){
  # put back in the missing group proportion, as 1-sum(others):
  # note that x is now of length (I*K)-1. 
  ws = append(x[1:12], 1-sum(x[1:12]), after = idx-1)
  rs = x[13:25]
  sum(ws*rs)
}
```

We can then remove a given subgroup proportion: 
```{r}
# 3rd subgroup weight is missing: 
hres_sub3 <- horiuchi(func = aggrfunc_sub,
                 pars1 = pop1[c(1:2,4:26)],
                 pars2 = pop2[c(1:2,4:26)],
                 N = 100,
                 idx = 3)

# 4th subgroup weight is missing: 
hres_sub4 <- horiuchi(func = aggrfunc_sub,
                 pars1 = pop1[c(1:3,5:26)],
                 pars2 = pop2[c(1:3,5:26)],
                 N = 100,
                 idx = 4)
```

The overall marginal totals remain the same: 
```{r}
# full vector
sum(hres0[1:13]);sum(hres0[14:26])
# missing group 3 prop
sum(hres_sub3[1:12]);sum(hres_sub3[13:25])
# missing group 4 prop:
sum(hres_sub4[1:12]);sum(hres_sub4[13:25])
```

But the individual contributions for the subgroups are different: 
```{r}
cbind(
  full_w = hres0[1:13],
  sub3_w = append(hres_sub3[1:12], NA, after=2),
  sub4_w = append(hres_sub4[1:12], NA, after=3)
) |> 
  as.data.frame() |> plot()
```


We can attempt the same using Das Gupta's approach, removing a sub-group proportion and including the sum to 1 constraint within the calculation of the rate:  
```{r}
dgfunc <- function(size,rate,idx){
  size[idx] <- 1-sum(size)
  size*rate
}
```

Because `dgnpop()` takes a dataframe object, and it doesn't like missing data, we can set the omitted group proportion as zero in both populations. 
```{r}
# 3rd subgroup weight is missing: 
dfA <- df
dfA$size[df$age_group=="25-29"] <- 0

dgres_sub3 <- 
  dgnpop(dfA,
       pop="pop", factors=c("size","rate"),
       id_vars = "age_group",
       ratefunction = "dgfunc(size,rate,3)",agg=FALSE) |>
  select(-std.set) |>
  pivot_wider(names_from=factor,values_from=rate) |>
  pivot_wider(names_from=pop,values_from=c(size,rate)) |>
  transmute(
    size = size_1985-size_1970,
    rate = rate_1985-rate_1970
  )

# 4th subgroup weight is missing: 
dfA <- df
dfA$size[df$age_group=="30-34"] <- 0

dgres_sub4 <- 
  dgnpop(dfA,
       pop="pop", factors=c("size","rate"),
       id_vars = "age_group",
       ratefunction = "dgfunc(size,rate,4)",agg=FALSE) |>
  select(-std.set) |>
  pivot_wider(names_from=factor,values_from=rate) |>
  pivot_wider(names_from=pop,values_from=c(size,rate)) |>
  transmute(
    size = size_1985-size_1970,
    rate = rate_1985-rate_1970
  )
```

Again, the overall marginal totals match:
```{r}
# full data
colSums(dgres0)
# missing group 1 prop
colSums(dgres_sub3)
# missing group 2 prop:
colSums(dgres_sub4)
```

And in this case, the subgroup specific contributions are invariant to which groups proportion was omitted:
```{r}
cbind(
  full_w = dgres0$size,
  sub3_w = dgres_sub3$size,
  sub4_w = dgres_sub4$size
) |> 
  as.data.frame() |> plot()
```

## retreiving Horiuchi's results with Das Gupta. 

To try and make Das Gupta's approach obtain the same subgroup specific contributions as Horiuchi, we need to reparameterise it slightly differently.

If we take a given subgroup, $j$, and express the subgroup proportion as: 
$$
P_j = 1 - \sum_{i \neq j} P_i
$$
Instead of expressing the crude rate as:  
$$
CR = \sum_{i} P_i \cdot R_i
$$
And we can expand this to:
$$
CR = R_j + \sum_{i \neq j} P_i (R_i - R_j)
$$
Provided we store $R_j$ in a separate column, we can then remove the row for subgroup $j$ entirely from the dataset: 

```{r}
dfA <- df |> 
  group_by(pop) |>
  mutate(
    ratej = rate[age_group == "25-29"],
    rate_excess = rate-ratej
  ) |> ungroup() |>
  filter(age_group != "25-29")
```

The tricky part of forcing this into Das Gupta's approach is that while we separate out the reference subgroup $j$'s rate into a distinct component in the calculation of the rate, the number of factors we want to consider for the decomposition hasn't increased. Using `factors = c("ratej","size","rate_excess")` will do a 3 factor decomposition, whereas we only want 2.  

A slightly hacky solution is to create a list column containing both the $rate-rate_j$ values as well as the value of $rate_j$. That way  we preserve having just 2 factors (each column is treated as a factor in `dgnpop()`):  

```{r}
dfA <- 
  dfA |> 
  mutate(
    listrate = map2(rate_excess, ratej,~list(..1,..2))
  )
```

We now have a `listrate` column where each entry is a list of length 2, with the 2nd entry being the reference group $j$'s rate. 

Inside the function we give to calculate the rate, we can then `unlist()` this, and get a vector for which the even entries are all just the value of $rate_j$, and the odd entries are $rate_i - rate_j$. 

So we can do the same decomposition as previously, but now using:  
```{r}
dgnpop(dfA, 
       pop="pop", 
       factors=c("size","listrate"),
       id_vars = "age_group",
       ratefunction = "unlist(listrate)[2] +
              sum(size * unlist(listrate)[seq(1,24,2)])")  |>
  dg_table()
```

And the subgroup specific contributions will match those of Horiuchi (when we omit subgroup $j$ from Horiuchi): 

```{r}
#| code-fold: true
dgres_sub3B <- 
  dgnpop(dfA, 
       pop="pop", 
       factors=c("size","listrate"),
       id_vars = "age_group",
       # remove the sum() because we don't want aggregate-level:
       ratefunction = "unlist(listrate)[2] +
              size * unlist(listrate)[seq(1,24,2)]",
       agg = FALSE) |>
  select(-std.set) |>
  pivot_wider(names_from=factor,values_from=rate) |>
  pivot_wider(names_from=pop,values_from=c(size,listrate)) |>
  transmute(
    size = size_1985-size_1970,
    rate = listrate_1985-listrate_1970
  )

cbind(
  DG = dgres_sub3B$size, 
  H = hres_sub3[1:12]
) |> plot()
```


## demonstrating the divergence

To demonstrate where these two methods diverge, consider 2 scenarios, for each of which there are two populations, 20 subgroups, and 3 factors (the first of these are relative sizes of subgroups). 

```{r}
#| code-fold: true
## Data: 
sdata <- simdata(nK=2,nI=20)
```

- Scenario 1: population rates are calculated as straightforward products: $R = \sum_i a_i \cdot b_i \cdot c_i$  
- Scenario 2: population rates are calculated as: $R = \sum_i a_i \cdot \frac{b_i}{\sum b} \cdot c_i$. This involves a cross-group dependency, in that the contribution of $b_i$ is dependent on the values that other groups have for $b$. (Note that we use $b$ here because it is *not* constrained to sum to 1, unlike $a$ which in our simulation is the subgroup proportions, and for which $\frac{a_i}{\sum a} = a_i$). 


**Scenario 1**  

```{r}
#| code-fold: true
## Das Gupta: 
dfdg <- cbind(
  pop = rep(c("pop1","pop2"),e=20),
  sgroup = rep(1:20,2),
  rbind(
    as.data.frame(matrix(sdata[[1]],ncol=3)),
    as.data.frame(matrix(sdata[[2]],ncol=3))
  )
)
names(dfdg)[3:5] <- letters[1:3]

dg_res <- 
  dgnpop(dfdg, pop = "pop", 
         factors = c("a","b","c"),
         id_vars = "sgroup", 
         ratefunction = "a*b*c", 
         agg=FALSE) |>
  pivot_wider(names_from=factor,values_from=rate) |>
  select(-std.set) |>
  pivot_wider(names_from=pop,values_from=c(a,b,c)) |>
  transmute(
    a_diff = a_pop2-a_pop1,
    b_diff = b_pop2-b_pop1,
    c_diff = c_pop2-c_pop1
  )


## Horiuchi:  
pop1 = sdata[[1]]
pop2 = sdata[[2]]

aggrfunc = function(x){
    x <- matrix(x, ncol = 3)
    sum(x[,1] * x[,2] * x[,3])
}

hres <- horiuchi(func = aggrfunc,
                  pars1 = pop1,
                  pars2 = pop2,
                  N = 100)

hres <- matrix(hres, ncol = 3)
```

The marginal sums of subgroup contributions are very close (as seen above). 
```{r}
# horiuchi:
colSums(hres)
# das gupta:
colSums(dg_res)
```

And the individual subgroup effects are also similar:
```{r}
#| code-fold: true
par(mfrow=c(1,3))
cbind(DG=dg_res[[1]], H=hres[,1]) |> plot(main="a")
cbind(DG=dg_res[[2]], H=hres[,2]) |> plot(main="b")
cbind(DG=dg_res[[3]], H=hres[,3]) |> plot(main="c")
```

**Scenario 2**  

```{r}
#| code-fold: true
dg_res1 <- 
  dgnpop(dfdg, 
         pop = "pop", 
         factors = c("a","b","c"),
         id_vars = "sgroup", 
         ratefunction = "a * (b / sum(b)) * c", agg=FALSE) |>
  pivot_wider(names_from=factor,values_from=rate) |>
  select(-std.set) |>
  pivot_wider(names_from=pop,values_from=c(a,b,c)) |>
  transmute(
    a_diff = a_pop2-a_pop1,
    b_diff = b_pop2-b_pop1,
    c_diff = c_pop2-c_pop1
  )

pop1 = sdata[[1]]
pop2 = sdata[[2]]

aggrfunc = function(x){
    x <- matrix(x, ncol = 3)
    sum(x[,1] * (x[,2] / sum(x[,2])) * x[,3])
}
hres1 <- horiuchi(func = aggrfunc,
                  pars1 = pop1,
                  pars2 = pop2,
                  N = 100)
hres1 <- matrix(hres1, ncol = 3)
```

Here we start to see differences in both marginal totals (slightly more so for $b$), and subgroup specific $b$ contributions: 
```{r}
# horiuchi:
colSums(hres1)
# das gupta: 
colSums(dg_res1)
```

```{r}
#| code-fold: true
par(mfrow=c(1,3))
cbind(DG=dg_res1[[1]], H=hres1[,1]) |> plot(main="a")
cbind(DG=dg_res1[[2]], H=hres1[,2]) |> plot(main="b")
cbind(DG=dg_res1[[3]], H=hres1[,3]) |> plot(main="c")
```
